---
title: "COVID -19 Overview"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

```{r load-packages, include=FALSE}
library(dplyr)
library(tidyr)
library(ggplot2)
library(lubridate)
library(knitr)
```


####Loading the COVID-19 data provided by John Hopkins University in GitHub
```{r}

cases<-read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_time_series/time_series_covid19_confirmed_global.csv",
                encoding = "UTF-8", check.names = FALSE)

head(cases)

```


We are using map_data function to get the "world" data to plot our cases data over it.
```{r}
#Loading World Map
world <- map_data("world")

#mybreaks created to use in map
mybreaks <- c(100, 500, 1000, 5000, 10000, 50000, 100000, 200000, 300000)


```


```{r,warning=FALSE, fig.width=10}
#Plotting the Global total cases

ggplot() +
  geom_polygon(data = world, aes(x=long, y = lat, group = group), fill="grey", alpha=0.3) +
  geom_point(data=cases, aes(x=Long, y=Lat, size=`4/5/20`, color=`4/5/20`),stroke=F, alpha=0.7) +
  scale_size_continuous(name="Cases", range=c(1,7),breaks=mybreaks, labels = c("1-499", "500-999", "1000-4999", "5,000-9,999","10,000-49,999", "50,000-99,999","100,000-199,999", "200,000-299,999", "300,000+")) +
  scale_color_viridis_c(option="inferno",name="Cases",breaks=mybreaks, labels = c("1-499", "500-999", "1000-4999", "5,000-9,999","10,000-49,999", "50,000-99,999","100,000-199,999", "200,000-299,999", "300,000+")) +
  theme_void() + 
  guides( colour = guide_legend()) +
  labs(caption = "Data Repository provided by Johns Hopkins CSSE. Visualization by DataScience+ ") +
  theme(
    legend.position = "bottom",
    text = element_text(color = "#22211d"),
    plot.background = element_rect(fill = "#ffffff", color = NA), 
    panel.background = element_rect(fill = "#ffffff", color = NA), 
    legend.background = element_rect(fill = "#ffffff", color = NA)
  )
```


###Confirmed Cases Globally
```{r}

gc<-read.csv("https://raw.githubusercontent.com/CSSEGISandData/COVID-19/master/csse_covid_19_data/csse_covid_19_daily_reports/04-21-2020.csv")

summary(gc)

gc_summ<- gc %>% group_by(Country_Region) %>% 
                  summarise(Total.Confirmed=sum(Confirmed), Total.Deaths=sum(Deaths),
                            Total.Recovered=sum(Recovered)) %>%
                  mutate(recovered_pct=(Total.Recovered/Total.Confirmed)*100,
                             deaths_pct=(Total.Deaths/Total.Confirmed)*100)%>%
                  arrange(desc(Total.Confirmed))
```


####Top 20 and Bottom 20 Countries with Total Confirmed Cases
######(Last Data Updated Date: April 4,2020)
```{r,message=FALSE}
(gc_top20 <-gc_summ %>% top_n(20,Total.Confirmed))
(gc_bottom20 <- gc_summ %>% arrange(Total.Confirmed) %>% head(20))

```
#####Plotting Top 20 countries with most confirmed cases with the recovery and deaths percent in those countries
```{r}

gc_top20%>% ggplot(aes(y=Total.Confirmed, x=reorder(Country_Region,Total.Confirmed))) +geom_col()+coord_flip() +
            ggtitle("Total Confirmed Cases Globally") +
            xlab("Country") + ylab("Confrimed Numbers")


gc_top20 %>% select(Country_Region, recovered_pct,deaths_pct) %>%
              gather(Cases,Percent,recovered_pct:deaths_pct) %>% 
              ggplot(aes(y=Percent, x=reorder(Country_Region,Percent), fill=Cases)) +geom_col(position = "dodge") + coord_flip()+
              ggtitle("Top 20 Countries with Highest Number of Cases") +
              xlab("Countries ") +
              ylab("Death/Receovered Percent") +
              theme(legend.position = "bottom")

gc_top20 %>% ggplot(aes(recovered_pct, deaths_pct,color=Country_Region)) + 
  geom_point() +
  theme(legend.position = "bottom")

#gc_top20%>% ggplot(aes(y=recovered_pct, x=Country_Region)) +geom_col()+coord_flip() 
#gc_top20%>% ggplot(aes(y=deaths_pct, x=Country_Region)) +geom_col()+coord_flip() 

```


#####Looking more into US
```{r}
library(maps)

us_map<-map_data("state")
US<-gc %>% filter(Country_Region=="US")


US_break <- c(1, 100, 1000, 5000, 10000, 25000, 50000,75000, 100000, 150000)

ggplot() +geom_polygon(data=us_map, aes(x=long, y=lat, group=group),
                       fill="gray97", color="grey75") + 
  coord_quickmap() +
  geom_point(data=filter(US, between(Long_,-130,-65), between(Lat,25,50)),
             aes(x=Long_, y=Lat, size=Confirmed, color="red"), alpha=0.4) +
  scale_size_area(breaks=US_break,max_size = 15) +
  theme(legend.position = "bottom",
        panel.background = element_rect( color = NA))

```

```{r}

ny_map<-us_map %>% filter(region=="new york")

ny<-US %>% filter(Province_State=="New York")

#counties<- map_data("county")
#ny_county <- counties %>% filter(region == "new york")

#ggplot() +geom_polygon(data=NY_map, aes(x=long, y=lat, group=group)) + 
 # coord_quickmap() + geom_polygon(color = "black", fill = "gray") +
  #theme_void()+
  #geom_polygon(data=ny_county,aes(x=long,y=lat, group=group), fill=NA, color="white")+
  #geom_polygon(data = ny, aes(x=Long_, y=Lat,group=FIPS,fill=Confirmed), color = "white") +
   #    coord_quickmap(xlim=c(-75, -82),ylim=c(36, 46))+
   #scale_fill_gradient(trans = "log10")
      

ny_cases<- cases %>% filter(`Province/State`=="New york")

#helpful links
#https://eriqande.github.io/rep-res-eeb-2017/map-making-in-R.html#maps-package-and-ggplot
#https://cran.r-project.org/web/packages/usmap/vignettes/mapping.html
#https://www.kaggle.com/mcnamamj/wisconsin


```






























